---
title: "lab4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab4)
```

# About this package:

This package contains the tasks of lab4 including linreg and theme making task

## Linreg class
input to this class is formula and data and the class contains various methods to compute various statistical parameters like tvalues, pvalues, residuals etc



1. **pred()**

This function returns the predicted values (P values)

Example:
```
pval<- linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris)
pval$pred()
```
2. **coef()**

This function returns coefficients as a named vector

3. **summary()**

This function returns the summary of linear regression model


4. **print()**

this function displays formula, data name and  RegressionCoefficientMatrix:

 
5. **plot()**

This function plots the graph of residuals vs Fitted values


6. **resid()**

This function returns vector of residuals


